---
title: "An Example of Using Bangdiwala Chart"
author: 
- Chaitra Nagaraja
- Haikady Nagaraja
- Pankaj Choudhary
- Hongbo Yang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{An Example of Using Bangdiwala Chart}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Load The Package

Install the package from CRAN.
```{r,eval=FALSE, install_cran}
install.packages("BangdiwalaChart")
```

To get the latest development version from GitHub:

```{r, eval=FALSE, install}
# install.packages('devtools')
devtools::install_github('hongbo-yang/BangdiwalaChart')
```

Load the package.
```{r,eval=FALSE,loadlib}
library(BangdiwalaChart)
```

## Information on Bangdiwala Chart

Constructed using "The agreement chart" by Shrikant I Bangdiwala. To learn more about Bangdiwala Chart, see
<http://www.stat.ncsu.edu/information/library/mimeo.archive/ISMS_1988_1859.pdf>, and
book: <http://www.utdallas.edu/~pkc022000/agreement_book/> chapter 12: Categorical Data.

## Example

#### Multiple Sclerosis Data 

MS Patients data (New Orelans and Winnipeg patients combined).
For original data, see: 
(1) Westlund, K. B. and Kurland, L. T. (1953). Studies on multiple sclerosis in Winnipeg, Manitoba, and New Orleans, Louisiana I. Prevalence; comparison between the patient groups in Winnipeg and New Orleans. American Journal of Hygiene 57, 380–396.
(2) MSPatients in vcd R package. 

```{r fig1, fig.height=5,fig.width=6}
library(BangdiwalaChart)
data.x <-matrix(c(43, 36, 12, 4,
                  8, 22, 27, 9, 
                  0, 7, 8, 7, 
                  1, 0, 10, 24), nrow=4, byrow=FALSE)
dimnames(data.x) <- list("neurologist 1 rating"=c(1:4),
                         "neurologist 2 rating"=c(1:4))
data.x <- as.table(t(data.x))		

bangdiwala_chart(x=data.x, main=NULL, add.B.hat=FALSE)

```

